Exploring dimensions of biodiversity in Japanese ferns

### 2021-06-30 ms/manuscript.Rmd
Remove model stats tables

All biodiversity metrics except for SES of RFD showed a significant relationship with temperature (`r table("env-model-params")`).

@@

```{r env-model-params-prep}
# Format model parameter summary for nice printing as a table
env_model_params_pretty <-
env_model_params %>%
  # Remove intercept
  filter(term != "(Intercept)") %>%
  # Double check that log-likelihood of null model is less than full
  verify(all(loglik_null < loglik_full)) %>%
  select(resp_var, term, estimate, cond_se, t_value, p_value) %>%
  # Format response variable and fixed effect names to look nice
  left_join(resp_var_lookup, by = "resp_var") %>%
  select(-resp_var) %>%
  rename(resp_var = resp_var_pretty) %>%
  left_join(indep_var_lookup, by = "term") %>%
  select(-term) %>%
  rename(term = term_pretty) %>%
  # Round to 2 signif digits
  mutate(across(c(estimate, cond_se, t_value), ~signif(., 2))) %>%
  # Format p-value
  mutate(
    signif = if_else(p_value < 0.05, TRUE, FALSE),
    p_value = case_when(
      p_value < 0.0001 ~ "< 0.0001",
      TRUE ~ signif(p_value, 2) %>% as.character
    )
  ) %>%
  arrange(resp_var, term) %>%
  select(resp_var, term, estimate, cond_se, t_value, p_value, signif)
```

```{r env-model-params-doc, results = "asis", eval = params$doc_type == "doc"}
env_model_params_pretty %>%
  mutate(
    across(where(is.numeric), as.character)) %>%
  rename("*t*-value" = t_value, "*p*-value" = p_value, "Variable" = term, "Estimate" = estimate, "Conditional SE" = cond_se) %>%
  as_grouped_data(groups = "resp_var") %>%
  as_flextable(hide_grouplabel = TRUE, col_keys = c("Variable", "Estimate", "Conditional SE", "*t*-value", "*p*-value")) %>%
  bold(i = ~ signif == TRUE, bold = TRUE)
```

```{r env-model-params-pdf, results = "asis", eval = params$doc_type == "pdf"}
# Define row groups
kbl_groups <-
env_model_params_pretty %>%
  transmute(resp_var, row_num = 1:nrow(.)) %>%
  group_by(resp_var) %>%
  summarize(start = min(row_num), end = max(row_num), .groups = "drop") %>%
  split(.$resp_var)

signif_rows <- env_model_params_pretty %>% pull(signif) %>% which()

env_model_params_pretty %>%
  mutate(
    across(where(is.numeric), as.character)) %>%
  rename("*t*-value" = t_value, "*p*-value" = p_value, "Variable" = term, "Estimate" = estimate, "Conditional SE" = cond_se) %>%
  select(-resp_var, -signif) %>%
  kbl(booktabs = TRUE) %>%
  kable_styling() %>%
  pack_rows(kbl_groups[[1]]$resp_var, kbl_groups[[1]]$start, kbl_groups[[1]]$end) %>%
  pack_rows(kbl_groups[[2]]$resp_var, kbl_groups[[2]]$start, kbl_groups[[2]]$end) %>%
  pack_rows(kbl_groups[[3]]$resp_var, kbl_groups[[3]]$start, kbl_groups[[3]]$end) %>%
  pack_rows(kbl_groups[[4]]$resp_var, kbl_groups[[4]]$start, kbl_groups[[4]]$end) %>%
  pack_rows(kbl_groups[[5]]$resp_var, kbl_groups[[5]]$start, kbl_groups[[5]]$end) %>%
  pack_rows(kbl_groups[[6]]$resp_var, kbl_groups[[6]]$start, kbl_groups[[6]]$end) %>%
  row_spec(row = signif_rows, bold = TRUE)
```

**`r table("env-model-params")`**. Parameter estimates of the effect of environmental variables on biodiversity metrics in the ferns of Japan. Significant effects (*p* < 0.05) in bold; significance assessed with likelihood ratio tests (see Methods). All models include random effect of geographical coordinates.

>>>>

All spatial models were significant relative to null models without any fixed effects. The effect of temperature dominated in most models, with only SES of PD showing a stronger effect of precipitation seasonality. Models fit using % apomictic taxa instead of temperature had lower cAIC, indicating a better fit. Biodiversity metrics with a genetic component (SES of PD, SES of RPD) each had a large, negative relationship with % apomictic taxa.

@@
